Multisensor Architecture for an Intersection Management System

### 2019-01-22 last_version.tex
Added information about contribution in section 4.1 (Articles, events and journals)
Updated link for last version downloading

Check for an updated version at github: 
\href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}

@@

	\begin{itemize}
	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
	\item Fixed V2I description in figure 1.6 (1.2.1)
	\item Reworded description of processing stages in section 2.1.1
	\item Described three transportation simulation models (2.2.1)
	\end{itemize}

>>>>

Check for an updated version at github: 
\href{https://github.com/gustavovelascoh/msc-report/wiki}{Multisensor Architecture for an Intersection Management System}

@@

	\begin{itemize}
	\item Updated link for last version downloading
	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
	\item Fixed V2I description in figure 1.6 (1.2.1)
	\item Reworded description of processing stages in section 2.1.1
	\item Described three transportation simulation models (2.2.1)
	\item Added information about contribution in section 4.1 (Articles, events and journals)
	\end{itemize}
